---
title: "Sex differences in cooperation: A mammalian perspective"
subtitle: "Supplementary Materials"
author: "Jennifer E. Smith, Adrian V. Jaeggi, Rose Holmes, Joan B. Silk"
toc: true
output:
  pdf_document: default
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
```

\newpage
# Supplemental Results

## Model 1: No predictors
Full summary of Model 1, estimating the likelihood of female-only coalitions, male-only coalitions, and coalitions by both sexes, without any predictors. Note that coalitions by both sexes is the reference level, hence we are only estimating the probabilities of female only and male only coalitions. In order to differentiate coefficients of the female coalitions and male coalitions linear models, we here put the corresponding outcome in parentheses, e.g. Intercept (female bias). All estimates are on the log-odds scale and summarized by the median and 90% credible interval ("lwr90CI" - "upr90CI") of the posterior distribution.


**Table S1**: Predicting the probability of coalition formation by sex (Model 1)
```{r table s1}
library(knitr)
library(rethinking)
load("post_m1.robj")
s1<- data.frame(Parameter = c("Intercept (female bias)", "Intercept (male bias)", "Phylo SD (female bias)", "Phylo SD (male bias)"), Mean = c(round(median(post_m1$b_muFemales_Intercept),2), round(median(post_m1$b_muMales_Intercept),2), round(median(post_m1$sd_Genus_species__muFemales_Intercept),2), round(median(post_m1$sd_Genus_species__muMales_Intercept),2)), lwr90CI = c(round(HPDI(post_m1$b_muFemales_Intercept, prob=0.90)[1],2), round(HPDI(post_m1$b_muMales_Intercept, prob=0.90)[1],2), round(HPDI(post_m1$sd_Genus_species__muFemales_Intercept, prob=0.90)[1],2), round(HPDI(post_m1$sd_Genus_species__muMales_Intercept, prob=0.90)[1],2)), upr90CI = c(round(HPDI(post_m1$b_muFemales_Intercept, prob=0.90)[2],2), round(HPDI(post_m1$b_muMales_Intercept, prob=0.90)[2],2), round(HPDI(post_m1$sd_Genus_species__muFemales_Intercept, prob=0.90)[2],2), round(HPDI(post_m1$sd_Genus_species__muMales_Intercept, prob=0.90)[2],2)))
kable(s1)
```
## Model 2: Mixed-sex vs sex-segregated
Full summary of Model 2, estimating the likelihood of female-only coalitions, male-only coalitions, and coalitions by both sexes in mixed-sex vs sex-segregated species. Note that coalitions by both sexes is the reference level, hence we are only estimating the probabilities of female only and male only coalitions. Mixed-sex is the reference level for the predictor, hence coefficients for sex-segregated species give the change in probability when going from mixed-sex to sex-segregation. In order to differentiate coefficients of the female coalitions and male coalitions linear models, we here put the corresponding outcome in parentheses, e.g. Intercept (female bias). All estimates are on the log-odds scale and summarized by the median and 90% credible interval ("lwr90CI" - "upr90CI") of the posterior distribution.


**Table S2**: Coalition formation in mixed-sex vs sex-segregated species (Model 2)
```{r table s2}
load("post_m2.robj")
s2<- data.frame(Parameter = c("Intercept (female bias)", "Intercept (male bias)", "Sex-segregated (female bias)", "Sex-segregated (male bias)", "Phylo SD (female bias)", "Phylo SD (male bias)"), Mean = c(round(median(post_m2$b_muFemales_Intercept),2), round(median(post_m2$b_muMales_Intercept),2), round(median(post_m2$b_muFemales_SexCompositionsegregated),2), round(median(post_m2$b_muMales_SexCompositionsegregated),2),round(median(post_m2$sd_Genus_species__muFemales_Intercept),2), round(median(post_m2$sd_Genus_species__muMales_Intercept),2)), lwr90CI = c(round(HPDI(post_m2$b_muFemales_Intercept, prob=0.90)[1],2), round(HPDI(post_m2$b_muMales_Intercept, prob=0.90)[1],2),round(HPDI(post_m2$b_muFemales_SexCompositionsegregated, prob=0.90)[1],2), round(HPDI(post_m2$b_muMales_SexCompositionsegregated, prob=0.90)[1],2), round(HPDI(post_m2$sd_Genus_species__muFemales_Intercept, prob=0.90)[1],2), round(HPDI(post_m2$sd_Genus_species__muMales_Intercept, prob=0.90)[1],2)), upr90CI = c(round(HPDI(post_m2$b_muFemales_Intercept, prob=0.90)[2],2), round(HPDI(post_m2$b_muMales_Intercept, prob=0.90)[2],2),round(HPDI(post_m2$b_muFemales_SexCompositionsegregated, prob=0.90)[2],2), round(HPDI(post_m2$b_muMales_SexCompositionsegregated, prob=0.90)[2],2), round(HPDI(post_m2$sd_Genus_species__muFemales_Intercept, prob=0.90)[2],2), round(HPDI(post_m2$sd_Genus_species__muMales_Intercept, prob=0.90)[2],2)))
kable(s2)
```
\newpage
## Model 3: Primates vs non-primates
Full summary of Model 3, estimating the likelihood of female-only coalitions, male-only coalitions, and coalitions by both sexes in primates vs non-primates. Note that coalitions by both sexes is the reference level, hence we are only estimating the probabilities of female only and male only coalitions. Non-primate is the reference level for the predictor, hence coefficients for primates give the change in probability when going from non-primate to primate. In order to differentiate coefficients of the female coalitions and male coalitions linear models, we here put the corresponding outcome in parentheses, e.g. Intercept (female bias). All estimates are on the log-odds scale and summarized by the median and 90% credible interval ("lwr90CI" - "upr90CI") of the posterior distribution.


**Table S3**: Coalition formation in primates vs non-primates (Model 3)
```{r table s3}
load("post_m3.robj")
s3<- data.frame(Parameter = c("Intercept (female bias)", "Intercept (male bias)", "Primate (female bias)", "Primate (male bias)", "Phylo SD (female bias)", "Phylo SD (male bias)"), Mean = c(round(median(post_m3$b_muFemales_Intercept),2), round(median(post_m3$b_muMales_Intercept),2), round(median(post_m3$b_muFemales_Primate),2), round(median(post_m3$b_muMales_Primate),2),round(median(post_m3$sd_Genus_species__muFemales_Intercept),2), round(median(post_m3$sd_Genus_species__muMales_Intercept),2)), lwr90CI = c(round(HPDI(post_m3$b_muFemales_Intercept, prob=0.90)[1],2), round(HPDI(post_m3$b_muMales_Intercept, prob=0.90)[1],2),round(HPDI(post_m3$b_muFemales_Primate, prob=0.90)[1],2), round(HPDI(post_m3$b_muMales_Primate, prob=0.90)[1],2), round(HPDI(post_m3$sd_Genus_species__muFemales_Intercept, prob=0.90)[1],2), round(HPDI(post_m3$sd_Genus_species__muMales_Intercept, prob=0.90)[1],2)), upr90CI = c(round(HPDI(post_m3$b_muFemales_Intercept, prob=0.90)[2],2), round(HPDI(post_m3$b_muMales_Intercept, prob=0.90)[2],2),round(HPDI(post_m3$b_muFemales_Primate, prob=0.90)[2],2), round(HPDI(post_m3$b_muMales_Primate, prob=0.90)[2],2), round(HPDI(post_m3$sd_Genus_species__muFemales_Intercept, prob=0.90)[2],2), round(HPDI(post_m3$sd_Genus_species__muMales_Intercept, prob=0.90)[2],2)))
kable(s3)
```
\newpage
## Model 4: Predicting probability of female coalitions
Full summaries of Model 4 and its robustness checks, estimating the probability of female coalitions as a function of food defensibility and female philopatry. Note that both predictors are coded as yes/no, with no being the reference level, hence coefficients show the change in probability of female coalitions when the predictor takes on the value of yes. All estimates are on the log-odds scale and summarized by the median and 90% credible interval ("lwr90CI" - "upr90CI") of the posterior distribution.


**Table S4**: Socio-ecological predictors of female coalitions (Model 4)
```{r table s4}
load("post_m4.robj")
s4<- data.frame(Parameter = c("Intercept", "Food defensible = yes", "Female philopatry = yes", "Phylo SD"), Mean = c(round(median(post_m4$b_Intercept),2), round(median(post_m4$b_Food_resource_defendable),2), round(median(post_m4$b_f_philopatry),2), round(median(post_m4$sd_Genus_species__Intercept),2)), lwr90CI = c(round(HPDI(post_m4$b_Intercept, prob=0.90)[1],2), round(HPDI(post_m4$b_Food_resource_defendable, prob=0.90)[1],2),round(HPDI(post_m4$b_f_philopatry, prob=0.90)[1],2), round(HPDI(post_m4$sd_Genus_species__Intercept, prob=0.90)[1],2)), upr90CI = c(round(HPDI(post_m4$b_Intercept, prob=0.90)[2],2), round(HPDI(post_m4$b_Food_resource_defendable, prob=0.90)[2],2),round(HPDI(post_m4$b_f_philopatry, prob=0.90)[2],2), round(HPDI(post_m4$sd_Genus_species__Intercept, prob=0.90)[2],2)))
kable(s4)
```
**Table S4.a**: Food defensibility only
```{r table s4a}
load("post_m4a.robj")
s4a<- data.frame(Parameter = c("Intercept", "Food defensible = yes", "Phylo SD"), Mean = c(round(median(post_m4a$b_Intercept),2), round(median(post_m4a$b_Food_resource_defendable),2), round(median(post_m4a$sd_Genus_species__Intercept),2)), lwr90CI = c(round(HPDI(post_m4a$b_Intercept, prob=0.90)[1],2), round(HPDI(post_m4a$b_Food_resource_defendable, prob=0.90)[1],2), round(HPDI(post_m4a$sd_Genus_species__Intercept, prob=0.90)[1],2)), upr90CI = c(round(HPDI(post_m4a$b_Intercept, prob=0.90)[2],2), round(HPDI(post_m4a$b_Food_resource_defendable, prob=0.90)[2],2), round(HPDI(post_m4a$sd_Genus_species__Intercept, prob=0.90)[2],2)))
kable(s4a)
```
**Table S4.b**: Female philopatry only
```{r table s4b}
load("post_m4b.robj")
s4b<- data.frame(Parameter = c("Intercept", "Female philopatry = yes", "Phylo SD"), Mean = c(round(median(post_m4b$b_Intercept),2), round(median(post_m4b$b_f_philopatry),2), round(median(post_m4b$sd_Genus_species__Intercept),2)), lwr90CI = c(round(HPDI(post_m4b$b_Intercept, prob=0.90)[1],2), round(HPDI(post_m4b$b_f_philopatry, prob=0.90)[1],2), round(HPDI(post_m4b$sd_Genus_species__Intercept, prob=0.90)[1],2)), upr90CI = c(round(HPDI(post_m4b$b_Intercept, prob=0.90)[2],2), round(HPDI(post_m4b$b_f_philopatry, prob=0.90)[2],2), round(HPDI(post_m4b$sd_Genus_species__Intercept, prob=0.90)[2],2)))
kable(s4b)
```

\newpage
## Model 5: Predicting probability of male coalitions
Full summaries of Model 5 and its robustness checks, estimating the probability of male coalitions as a function of sexual dimorphism and male philopatry. Note that sexual dimorphism is centered on 1 (i.e. monomorphic) and units are standard deviations; male philopatry is coded as yes/no, with no being the reference level. Hence coefficients show the change in probability of male coalitions with a 1SD change in dimorphism or when male philopatry takes on the value of yes. All estimates are on the log-odds scale and summarized by the median and 90% credible interval ("lwr90CI" - "upr90CI") of the posterior distribution.


**Table S5**: Socio-ecological predictors of male coalitions (Model 5)
```{r table s5}
load("post_m5.robj")
s5<- data.frame(Parameter = c("Intercept", "Sexual dimorphism", "Male philopatry = yes", "Phylo SD"), Mean = c(round(median(post_m5$b_Intercept),2), round(median(post_m5$b_SexDim.z),2), round(median(post_m5$b_m_philopatry),2), round(median(post_m5$sd_Genus_species__Intercept),2)), lwr90CI = c(round(HPDI(post_m5$b_Intercept, prob=0.90)[1],2), round(HPDI(post_m5$b_SexDim.z, prob=0.90)[1],2),round(HPDI(post_m5$b_m_philopatry, prob=0.90)[1],2), round(HPDI(post_m5$sd_Genus_species__Intercept, prob=0.90)[1],2)), upr90CI = c(round(HPDI(post_m5$b_Intercept, prob=0.90)[2],2), round(HPDI(post_m5$b_SexDim.z, prob=0.90)[2],2),round(HPDI(post_m5$b_m_philopatry, prob=0.90)[2],2), round(HPDI(post_m5$sd_Genus_species__Intercept, prob=0.90)[2],2)))
kable(s5)
```
**Table S5.a**: Sexual dimorphism only
```{r table s5a}
load("post_m5a.robj")
s5a<- data.frame(Parameter = c("Intercept", "Sexual dimorphism", "Phylo SD"), Mean = c(round(median(post_m5a$b_Intercept),2), round(median(post_m5a$b_SexDim.z),2), round(median(post_m5a$sd_Genus_species__Intercept),2)), lwr90CI = c(round(HPDI(post_m5a$b_Intercept, prob=0.90)[1],2), round(HPDI(post_m5a$b_SexDim.z, prob=0.90)[1],2), round(HPDI(post_m5a$sd_Genus_species__Intercept, prob=0.90)[1],2)), upr90CI = c(round(HPDI(post_m5a$b_Intercept, prob=0.90)[2],2), round(HPDI(post_m5a$b_SexDim.z, prob=0.90)[2],2), round(HPDI(post_m5a$sd_Genus_species__Intercept, prob=0.90)[2],2)))
kable(s5a)
```
**Table S5.b**: Male philopatry only
```{r table s5b}
load("post_m5b.robj")
s5b<- data.frame(Parameter = c("Intercept", "Male philopatry = yes", "Phylo SD"), Mean = c(round(median(post_m5b$b_Intercept),2), round(median(post_m5b$b_m_philopatry),2), round(median(post_m5b$sd_Genus_species__Intercept),2)), lwr90CI = c(round(HPDI(post_m5b$b_Intercept, prob=0.90)[1],2), round(HPDI(post_m5b$b_m_philopatry, prob=0.90)[1],2), round(HPDI(post_m5b$sd_Genus_species__Intercept, prob=0.90)[1],2)), upr90CI = c(round(HPDI(post_m5b$b_Intercept, prob=0.90)[2],2), round(HPDI(post_m5b$b_m_philopatry, prob=0.90)[2],2), round(HPDI(post_m5b$sd_Genus_species__Intercept, prob=0.90)[2],2)))
kable(s5b)
```



```{r Figure S1, eval=FALSE}
## pre-processing: compute predicted probabilities from models 4 & 5
# --> for simplicity, use m4/5 a&b so that predictions are not conditional on other covariates (and no need to marginalize over them given that they're competing causes rather than confounders and results are virtually the same as m4)

# Model 4a: Food defensibility
p_fcoal_nd<- logistic(post_m4a$b_Intercept)
p_fcoal_def<- logistic(post_m4a$b_Intercept+post_m4a$b_Food_resource_defendable)

# Model 4b: Female philopatry
p_fcoal_nphilo<- logistic(post_m4b$b_Intercept)
p_fcoal_fphilo<- logistic(post_m4b$b_Intercept+post_m4b$b_f_philopatry)


# Model 5a: Dimorphism
p_mcoal_mono<- logistic(post_m5a$b_Intercept)
p_mcoal_dim<- logistic(post_m5a$b_Intercept+post_m5a$b_SexDim.z)

# Model 5b: male philopatry
p_mcoal_nphilo<- logistic(post_m5b$b_Intercept)
p_mcoal_mphilo<- logistic(post_m5b$b_Intercept+post_m5b$b_m_philopatry)


## prepare plotting
library(MetBrewer)
col.pred1<- MetPalettes$Lakota[[1]][2]
col.pred2<- MetPalettes$Lakota[[1]][3]


tiff("Figure S1.tif", compression = "lzw", 
       height = 12.0, width = 12.0, units = "cm", res = 600, pointsize = 5)
# 2 x 2 figure panel
par(mfrow=c(2,2))
# a) female coalitions food
dens(p.m1[[1]][,1], xlab="Predicted probability", ylab="Density", main="a) Female coalitions: Food", col="white", ylim=c(0,2.5), xlim=c(0,1), cex.main=1.5, cex.axis=1.5, cex.lab=1.5)
polygon(density(p_fcoal_nd), col=adjustcolor(col.pred1, alpha.f=0.5))
polygon(density(p_fcoal_def), col=adjustcolor(col.pred2, alpha.f=0.5))
legend("topleft", fill=c(adjustcolor(col.pred1, alpha.f=0.5), adjustcolor(col.pred2, alpha.f=0.5)), border="black", legend=c("Non-defensible", "Defensible"), bty="n", cex=1.5)

# b) female coalitions philopatry
dens(p.m1[[1]][,1], xlab="Predicted probability", ylab="Density", main="b) Female coalitions: Philopatry", col="white", ylim=c(0,2.5), xlim=c(0,1), cex.main=1.5, cex.axis=1.5, cex.lab=1.5)
polygon(density(p_fcoal_nphilo), col=adjustcolor(col.pred1, alpha.f=0.5))
polygon(density(p_fcoal_fphilo), col=adjustcolor(col.pred2, alpha.f=0.5))
legend("topleft", fill=c(adjustcolor(col.pred1, alpha.f=0.5), adjustcolor(col.pred2, alpha.f=0.5)), border="black", legend=c("Females disperse", "Females philopatric"), bty="n", cex=1.5)

# c) male coalitions dimorphism
dens(p.m1[[1]][,1], xlab="Predicted probability", ylab="Density", main="c) Male coalitions: Dimorphism", col="white", ylim=c(0,2.5), xlim=c(0,1), cex.main=1.5, cex.axis=1.5, cex.lab=1.5)
polygon(density(p_mcoal_mono), col=adjustcolor(col.pred1, alpha.f=0.5))
polygon(density(p_mcoal_dim), col=adjustcolor(col.pred2, alpha.f=0.5))
legend("topleft", fill=c(adjustcolor(col.pred1, alpha.f=0.5), adjustcolor(col.pred2, alpha.f=0.5)), border="black", legend=c("Monomorphic", "Dimorphic (+1SD)"), bty="n", cex=1.5)

# d) male coalitions philopatry
dens(p.m1[[1]][,1], xlab="Predicted probability", ylab="Density", main="d) Male coalitions: Philopatry", col="white", ylim=c(0,2.5), xlim=c(0,1), cex.main=1.5, cex.axis=1.5, cex.lab=1.5)
polygon(density(p_mcoal_nphilo), col=adjustcolor(col.pred1, alpha.f=0.5))
polygon(density(p_mcoal_mphilo), col=adjustcolor(col.pred2, alpha.f=0.5))
legend("topleft", fill=c(adjustcolor(col.pred1, alpha.f=0.5), adjustcolor(col.pred2, alpha.f=0.5)), border="black", legend=c("Males disperse", "Males philopatric"), bty="n", cex=1.5)

dev.off()

```