---
title: "Sex-bias coalitions results"
author: "Adrian Jaeggi"
date: "8 2 2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, include=FALSE, message=FALSE, warning=FALSE)
```

```{r loading}
 ## load relevant packages, set working directory, load saved model posteriors
library(brms)
library(rstan)
library(rethinking)
memory.limit(size=100000)
load("post_m1.robj")
load("post_m2.robj")
load("post_m3.robj")
load("post_m4.robj")
load("post_m4a.robj")
load("post_m4b.robj")
load("post_m5.robj")
load("post_m5a.robj")
load("post_m5b.robj")
d<- read.csv("sexbiascoalitions.csv", header=TRUE)
d$Primate<- 0
d$Primate[d$Order=="Primata"]<- 1

```

```{r post-processing posteriors}
# calculate phylogenetic signal for Model 1
VarPhy.female<-post_m1$sd_Genus_species__muFemalebiased_Intercept
VarPhy.male<-post_m1$sd_Genus_species__muMalebiased_Intercept
VarDistro<- pi^2/3
lambda.m1<- (VarPhy.female+VarPhy.male)/(VarPhy.female+VarPhy.male+VarDistro)

# compute predicted probabilities for Model 1
{    K <- 3 #number of character states used
  ns <- nrow(post_m1)
  n <- 1
  
  softmax2 <- function(x) {
    x <- max(x) - x
    exp(-x)/sum(exp(-x))
  }
  
  p.m1 <- list()
  
  for ( i in 1:n ) {
    p.m1[[i]] <- sapply( 1:K , function(k) {
      if ( k < K ) {
        ptemp <- post_m1[,k] 
      } else {
        ptemp <- rep(0,ns)
      }
      return(ptemp)
    })
    ## The values are converted to probabilities using the softmax function
    ## which ensures that the predicted values across categories sum to
    ## 100% probabilities.
    for ( s in 1:ns ) p.m1[[i]][s,] <- softmax2( p.m1[[i]][s,] )
  }
}
p_median.m1 <- sapply( 1:length(p.m1) , function(i) apply(p.m1[[i]],2,median) )
p_HPDI.m1 <- sapply( 1:length(p.m1) , function(i) apply(p.m1[[i]],2,HPDI, prob=0.90) )
pred_probs_m1<- cbind(p_median.m1, p_HPDI.m1[c(1,3,5),], p_HPDI.m1[c(2,4,6),])

# probability of difference
diff.fm.m1<- p.m1[[1]][,1]-p.m1[[1]][,2]

```

Contrary to our first prediction, females did not cooperate more in within-group coalitions than males (Fig. 1, Model 1, see also supplement). In fact, the probability of a female bias in coalitions (median = `r round(pred_probs_m1,2)[1,1]`, 90% credible interval = `r round(pred_probs_m1,2)[1,2]` - `r round(pred_probs_m1,2)[1,3]`) was virtually the same as the probability of a male bias (`r round(pred_probs_m1,2)[2,1]`, `r round(pred_probs_m1,2)[2,2]` - `r round(pred_probs_m1,2)[2,3]`) and the most likely state was unbiased coalition formation (`r round(pred_probs_m1,2)[3,1]`, `r round(pred_probs_m1,2)[3,2]` - `r round(pred_probs_m1,2)[3,3]`). Thus, only `r round(100*sum(diff.fm.m1>0)/length(diff.fm.m1),0)`% of the posterior probability supports our prediction of female bias being more likely than male bias, and none of the three possible states was greater than chance (% of posterior > 0.33 for female bias: `r round(100*sum(p.m1[[1]][,1]>0.33)/length(p.m1[[1]][,1]),0)`%; male bias: `r round(100*sum(p.m1[[1]][,2]>0.33)/length(p.m1[[1]][,2]),0)`%; unbiased: `r round(100*sum(p.m1[[1]][,3]>0.33)/length(p.m1[[1]][,3]),0)`%). The phylogenetic signal was weak (median λ = `r round(median(lambda.m1),2)`, 90% CI = `r round(HPDI(lambda.m1, prob=0.90)[1],2)` - `r round(HPDI(lambda.m1, prob=0.90)[2],2)`)). 

This general pattern did not change appreciably when comparing species living in mixed-sex groups (n = `r length(d$SexComposition[d$SexComposition=="mixed"])` species) with sex-segregated ones (n = `r length(d$SexComposition[d$SexComposition=="segregated"])` species; Model 2), or primates (n= `r length(d$Primate[d$Primate==1])` species) with non-primates (n= `r length(d$Primate[d$Primate==0])` species; Model 3). Specifically, the odds of female bias and male bias were essentially the same in sex-segregated species compared to mixed-sex species (female bias: median odds ratio = `r round(median(exp(post_m2$b_muFemalebiased_SexCompositionsegregated)),2)`, 90% CI = `r round(HPDI(exp(post_m2$b_muFemalebiased_SexCompositionsegregated), prob=0.90)[1],2)` - `r round(HPDI(exp(post_m2$b_muFemalebiased_SexCompositionsegregated), prob=0.90)[2],2)`, probability OR>1 = `r round(100*sum(post_m2$b_muFemalebiased_SexCompositionsegregated>0)/nrow(post_m2),0)`%; male bias: median OR = `r round(median(exp(post_m2$b_muMalebiased_SexCompositionsegregated)),2)`, 90% CI = `r round(HPDI(exp(post_m2$b_muMalebiased_SexCompositionsegregated), prob=0.90)[1],2)` - `r round(HPDI(exp(post_m2$b_muMalebiased_SexCompositionsegregated), prob=0.90)[2],2)`, probability OR>1 = `r round(100*sum(post_m2$b_muMalebiased_SexCompositionsegregated>0)/nrow(post_m2),0)`%) or primates compared to non-primates (female bias: median odds ratio = `r round(median(exp(post_m3$b_muFemalebiased_Primate)),2)`, 90% CI = `r round(HPDI(exp(post_m3$b_muFemalebiased_Primate), prob=0.90)[1],2)` - `r round(HPDI(exp(post_m3$b_muFemalebiased_Primate), prob=0.90)[2],2)`, probability OR>1 = `r round(100*sum(post_m3$b_muFemalebiased_Primate>0)/nrow(post_m3),0)`%; male bias: median OR = `r round(median(exp(post_m3$b_muMalebiased_Primate)),2)`, 90% CI = `r round(HPDI(exp(post_m3$b_muMalebiased_Primate), prob=0.90)[1],2)` - `r round(HPDI(exp(post_m3$b_muMalebiased_Primate), prob=0.90)[2],2)`, probability OR>1 = `r round(100*sum(post_m3$b_muMalebiased_Primate>0)/nrow(post_m3),0)`%). We therefore did not stratify our subsequent analyses by these variables.

To test our socio-ecological predictors we ran one binomial model on the presence of female coalitions (Model 4), including food defensibility (yes/no) and female philopatry (yes/no) as predictors, and one on the presence of male coalitions (Model 5), including sexual dimorphism and male philopatry (yes/no) as predictors. Note that for the purpose of these analyses we scored female philopatry when females or both sexes are philopatric, and male philopatry when males or both sexes are philopatric. As a robustness check, we also modeled each of these competing causes on its own. The probability of female coalitions was not not appreciably more likely in species with defensible food resources compared to species with non-defensible food resources (OR = `r round(median(exp(post_m4$b_Food_resource_defendable)),2)`, 90% CI = `r round(HPDI(exp(post_m4$b_Food_resource_defendable), prob=0.90)[1],2)` - `r round(HPDI(exp(post_m4$b_Food_resource_defendable), prob=0.90)[2],2)`, probability OR>1 = `r round(100*sum(post_m4$b_Food_resource_defendable>0)/nrow(post_m4),0)`%), or in species with female philopatry compared to female dispersal (OR = `r round(median(exp(post_m4$b_f_philopatry)),2)`, 90% CI = `r round(HPDI(exp(post_m4$b_f_philopatry), prob=0.90)[1],2)` - `r round(HPDI(exp(post_m4$b_f_philopatry), prob=0.90)[2],2)`, probability OR>1 = `r round(100*sum(post_m4$b_f_philopatry>0)/nrow(post_m4),0)`%). Likewise, the probability of male coalitions was only marginally higher in sexually dimorphic species (OR for 1SD change in dimorphism = `r round(median(exp(post_m5$b_SexDim.z)),2)`, 90% CI = `r round(HPDI(exp(post_m5$b_SexDim.z), prob=0.90)[1],2)` - `r round(HPDI(exp(post_m5$b_SexDim.z), prob=0.90)[2],2)`, probability OR>1 = `r round(100*sum(post_m5$b_SexDim.z>0)/nrow(post_m4),0)`%), and virtually the same whether males were philopatric or dispersed (OR = `r round(median(exp(post_m5$b_m_philopatry)),2)`, 90% CI = `r round(HPDI(exp(post_m5$b_SexDim.z), prob=0.90)[1],2)` - `r round(HPDI(exp(post_m5$b_m_philopatry), prob=0.90)[2],2)`, probability OR>1 = `r round(100*sum(post_m5$b_m_philopatry>0)/nrow(post_m4),0)`%). These inferences did not change when considering each predictor in a model on its own (see Supplement).

```{r Figure X}
## pre-processing: compute predicted probabilities from model 4
# --> for simplicity, use m4a-c so that predictions are not conditional on other covariates (and no need to marginalize over them given that they're competing causes rather than confounders and results are virtually the same as m4)

# Model 4a: Food defensibility
# not defensible
{    K <- 3 #number of character states used
  ns <- nrow(post_m4a)
  n <- 1
  
  softmax2 <- function(x) {
    x <- max(x) - x
    exp(-x)/sum(exp(-x))
  }
  
  p.m4a.nd <- list()
  
  for ( i in 1:n ) {
    p.m4a.nd[[i]] <- sapply( 1:K , function(k) {
      if ( k < K ) {
        ptemp <- post_m4a[,k] # intercept only = non - defensible
      } else {
        ptemp <- rep(0,ns)
      }
      return(ptemp)
    })
    ## The values are converted to probabilities using the softmax function
    ## which ensures that the predicted values across categories sum to
    ## 100% probabilities.
    for ( s in 1:ns ) p.m4a.nd[[i]][s,] <- softmax2( p.m4a.nd[[i]][s,] )
  }
}
colMeans(p.m4a.nd[[1]]) # quick check if reasonable
# defensible
{    K <- 3 #number of character states used
  ns <- nrow(post_m4a)
  n <- 1
  
  softmax2 <- function(x) {
    x <- max(x) - x
    exp(-x)/sum(exp(-x))
  }
  
  p.m4a.d <- list()
  
  for ( i in 1:n ) {
    p.m4a.d[[i]] <- sapply( 1:K , function(k) {
      if ( k < K ) {
        ptemp <- post_m4a[,k] + post_m4a[,k+2] # intercept + defensible
      } else {
        ptemp <- rep(0,ns)
      }
      return(ptemp)
    })
    ## The values are converted to probabilities using the softmax function
    ## which ensures that the predicted values across categories sum to
    ## 100% probabilities.
    for ( s in 1:ns ) p.m4a.d[[i]][s,] <- softmax2( p.m4a.d[[i]][s,] )
  }
}
colMeans(p.m4a.d[[1]]) # quick check if reasonable

# Model 4c: Sexual dimorphism
# monomorphic
{    K <- 3 #number of character states used
  ns <- nrow(post_m4c)
  n <- 1
  
  softmax2 <- function(x) {
    x <- max(x) - x
    exp(-x)/sum(exp(-x))
  }
  
  p.m4c.mono <- list()
  
  for ( i in 1:n ) {
    p.m4c.mono[[i]] <- sapply( 1:K , function(k) {
      if ( k < K ) {
        ptemp <- post_m4c[,k] # intercept only = monomorphic
      } else {
        ptemp <- rep(0,ns)
      }
      return(ptemp)
    })
    ## The values are converted to probabilities using the softmax function
    ## which ensures that the predicted values across categories sum to
    ## 100% probabilities.
    for ( s in 1:ns ) p.m4c.mono[[i]][s,] <- softmax2( p.m4c.mono[[i]][s,] )
  }
}
colMeans(p.m4c.mono[[1]]) # quick check if reasonable
# + 1SD dimorphic (males larger)
{    K <- 3 #number of character states used
  ns <- nrow(post_m4c)
  n <- 1
  
  softmax2 <- function(x) {
    x <- max(x) - x
    exp(-x)/sum(exp(-x))
  }
  
  p.m4c.dim <- list()
  
  for ( i in 1:n ) {
    p.m4c.dim[[i]] <- sapply( 1:K , function(k) {
      if ( k < K ) {
        ptemp <- post_m4c[,k] + post_m4c[,k+2] # intercept + SexDim.z
      } else {
        ptemp <- rep(0,ns)
      }
      return(ptemp)
    })
    ## The values are converted to probabilities using the softmax function
    ## which ensures that the predicted values across categories sum to
    ## 100% probabilities.
    for ( s in 1:ns ) p.m4c.dim[[i]][s,] <- softmax2( p.m4c.dim[[i]][s,] )
  }
}
colMeans(p.m4c.dim[[1]]) # quick check if reasonable

# Model 4b: Philopatry
# neither sex
{    K <- 3 #number of character states used
  ns <- nrow(post_m4b)
  n <- 1
  
  softmax2 <- function(x) {
    x <- max(x) - x
    exp(-x)/sum(exp(-x))
  }
  
  p.m4b.N <- list()
  
  for ( i in 1:n ) {
    p.m4b.N[[i]] <- sapply( 1:K , function(k) {
      if ( k < K ) {
        ptemp <- post_m4b[,k] # intercept only = monomorphic
      } else {
        ptemp <- rep(0,ns)
      }
      return(ptemp)
    })
    ## The values are converted to probabilities using the softmax function
    ## which ensures that the predicted values across categories sum to
    ## 100% probabilities.
    for ( s in 1:ns ) p.m4b.N[[i]][s,] <- softmax2( p.m4b.N[[i]][s,] )
  }
}
colMeans(p.m4b.N[[1]]) # quick check if reasonable
# both sexes
{    K <- 3 #number of character states used
  ns <- nrow(post_m4b)
  n <- 1
  
  softmax2 <- function(x) {
    x <- max(x) - x
    exp(-x)/sum(exp(-x))
  }
  
  p.m4b.B <- list()
  
  for ( i in 1:n ) {
    p.m4b.B[[i]] <- sapply( 1:K , function(k) {
      if ( k < K ) {
        ptemp <- post_m4b[,k] + post_m4b[,k*3] # intercept + philo = B [columns 3 and 6]
      } else {
        ptemp <- rep(0,ns)
      }
      return(ptemp)
    })
    ## The values are converted to probabilities using the softmax function
    ## which ensures that the predicted values across categories sum to
    ## 100% probabilities.
    for ( s in 1:ns ) p.m4b.B[[i]][s,] <- softmax2( p.m4b.B[[i]][s,] )
  }
}
colMeans(p.m4b.B[[1]]) # quick check if reasonable
# females
{    K <- 3 #number of character states used
  ns <- nrow(post_m4b)
  n <- 1
  
  softmax2 <- function(x) {
    x <- max(x) - x
    exp(-x)/sum(exp(-x))
  }
  
  p.m4b.F <- list()
  
  for ( i in 1:n ) {
    p.m4b.F[[i]] <- sapply( 1:K , function(k) {
      if ( k < K ) {
        ptemp <- post_m4b[,k] + post_m4b[,k*4-(k-1)] # intercept + philo = F [columns 4 and 7]
      } else {
        ptemp <- rep(0,ns)
      }
      return(ptemp)
    })
    ## The values are converted to probabilities using the softmax function
    ## which ensures that the predicted values across categories sum to
    ## 100% probabilities.
    for ( s in 1:ns ) p.m4b.F[[i]][s,] <- softmax2( p.m4b.F[[i]][s,] )
  }
}
colMeans(p.m4b.F[[1]]) # quick check if reasonable
# males
{    K <- 3 #number of character states used
  ns <- nrow(post_m4b)
  n <- 1
  
  softmax2 <- function(x) {
    x <- max(x) - x
    exp(-x)/sum(exp(-x))
  }
  
  p.m4b.M <- list()
  
  for ( i in 1:n ) {
    p.m4b.M[[i]] <- sapply( 1:K , function(k) {
      if ( k < K ) {
        ptemp <- post_m4b[,k] + post_m4b[,k+2*(k+1)] # intercept + philo = F [columns 5 and 8]
      } else {
        ptemp <- rep(0,ns)
      }
      return(ptemp)
    })
    ## The values are converted to probabilities using the softmax function
    ## which ensures that the predicted values across categories sum to
    ## 100% probabilities.
    for ( s in 1:ns ) p.m4b.M[[i]][s,] <- softmax2( p.m4b.M[[i]][s,] )
  }
}
colMeans(p.m4b.M[[1]]) # quick check if reasonable


## prepare plotting
library(MetBrewer)
col.female<- MetPalettes$Egypt[[1]][2]
col.male<- MetPalettes$Egypt[[1]][3]
col.both<- MetPalettes$Egypt[[1]][4]

tiff("Figure X.tif", compression = "lzw", 
       height = 12.0, width = 12.0, units = "cm", res = 600, pointsize = 5)
# 3 x 3 figure panel
par(mfrow=c(3,3))

# a) intercept only model
dens(p.m4a.nd[[1]][,1], xlab="Predicted probability", ylab="Density", main="a) No covariates", col="white", ylim=c(0,3), xlim=c(0,1), cex.main=1.5, cex.axis=1.2, cex.lab=1.2)
polygon(density(p.m1[[1]][,1]), col=adjustcolor(col.female, alpha.f=0.5))
polygon(density(p.m1[[1]][,2]), col=adjustcolor(col.male, alpha.f=0.5))
polygon(density(p.m1[[1]][,3]), col=adjustcolor(col.both, alpha.f=0.5))
legend("topright", fill=c(adjustcolor(col.female, alpha.f=0.5), adjustcolor(col.male, alpha.f=0.5), adjustcolor(col.both, alpha.f=0.5)), border="black", legend=c("Females only", "Males only", "Both sexes"), bty="n", cex=1.5)
# mtext("a)", cex=1.5, adj=0)
# b) food = not defensible
dens(p.m1[[1]][,1], xlab="Predicted probability", ylab="Density", main="b) Food = non-defensible", col="white", ylim=c(0,3), xlim=c(0,1), cex.main=1.5, cex.axis=1.2, cex.lab=1.2)
polygon(density(p.m4a.nd[[1]][,1]), col=adjustcolor(col.female, alpha.f=0.5))
polygon(density(p.m4a.nd[[1]][,2]), col=adjustcolor(col.male, alpha.f=0.5))
polygon(density(p.m4a.nd[[1]][,3]), col=adjustcolor(col.both, alpha.f=0.5))
legend("topright", fill=c(adjustcolor(col.female, alpha.f=0.5), adjustcolor(col.male, alpha.f=0.5), adjustcolor(col.both, alpha.f=0.5)), border="black", legend=c("Females only", "Males only", "Both sexes"), bty="n", cex=1.5)

# c) food = defensible
dens(p.m1[[1]][,1], xlab="Predicted probability", ylab="Density", main="c) Food = defensible", col="white", ylim=c(0,3), xlim=c(0,1), cex.main=1.5, cex.axis=1.2, cex.lab=1.2)
polygon(density(p.m4a.d[[1]][,1]), col=adjustcolor(col.female, alpha.f=0.5))
polygon(density(p.m4a.d[[1]][,2]), col=adjustcolor(col.male, alpha.f=0.5))
polygon(density(p.m4a.d[[1]][,3]), col=adjustcolor(col.both, alpha.f=0.5))
legend("topright", fill=c(adjustcolor(col.female, alpha.f=0.5), adjustcolor(col.male, alpha.f=0.5), adjustcolor(col.both, alpha.f=0.5)), border="black", legend=c("Females only", "Males only", "Both sexes"), bty="n", cex=1.5)

# d) sex dim = 0
dens(p.m1[[1]][,1], xlab="Predicted probability", ylab="Density", main="d) Monomorphic", col="white", ylim=c(0,3), xlim=c(0,1), cex.main=1.5, cex.axis=1.2, cex.lab=1.2)
polygon(density(p.m4c.mono[[1]][,1]), col=adjustcolor(col.female, alpha.f=0.5))
polygon(density(p.m4c.mono[[1]][,2]), col=adjustcolor(col.male, alpha.f=0.5))
polygon(density(p.m4c.mono[[1]][,3]), col=adjustcolor(col.both, alpha.f=0.5))
legend("topright", fill=c(adjustcolor(col.female, alpha.f=0.5), adjustcolor(col.male, alpha.f=0.5), adjustcolor(col.both, alpha.f=0.5)), border="black", legend=c("Females only", "Males only", "Both sexes"), bty="n", cex=1.5)

# e) sex dim = 1
dens(p.m1[[1]][,1], xlab="Predicted probability", ylab="Density", main="e) Dimorphic (+1SD)", col="white", ylim=c(0,3), xlim=c(0,1), cex.main=1.5, cex.axis=1.2, cex.lab=1.2)
polygon(density(p.m4c.dim[[1]][,1]), col=adjustcolor(col.female, alpha.f=0.5))
polygon(density(p.m4c.dim[[1]][,2]), col=adjustcolor(col.male, alpha.f=0.5))
polygon(density(p.m4c.dim[[1]][,3]), col=adjustcolor(col.both, alpha.f=0.5))
legend("topright", fill=c(adjustcolor(col.female, alpha.f=0.5), adjustcolor(col.male, alpha.f=0.5), adjustcolor(col.both, alpha.f=0.5)), border="black", legend=c("Females only", "Males only", "Both sexes"), bty="n", cex=1.5)

# f) philo = N
dens(p.m1[[1]][,1], xlab="Predicted probability", ylab="Density", main="f) Philopatry = Neither", col="white", ylim=c(0,3), xlim=c(0,1), cex.main=1.5, cex.axis=1.2, cex.lab=1.2)
polygon(density(p.m4b.N[[1]][,1]), col=adjustcolor(col.female, alpha.f=0.5))
polygon(density(p.m4b.N[[1]][,2]), col=adjustcolor(col.male, alpha.f=0.5))
polygon(density(p.m4b.N[[1]][,3]), col=adjustcolor(col.both, alpha.f=0.5))
legend("topright", fill=c(adjustcolor(col.female, alpha.f=0.5), adjustcolor(col.male, alpha.f=0.5), adjustcolor(col.both, alpha.f=0.5)), border="black", legend=c("Females only", "Males only", "Both sexes"), bty="n", cex=1.5)

# g) philo = F
dens(p.m1[[1]][,1], xlab="Predicted probability", ylab="Density", main="g) Philopatry = Females", col="white", ylim=c(0,3), xlim=c(0,1), cex.main=1.5, cex.axis=1.2, cex.lab=1.2)
polygon(density(p.m4b.F[[1]][,1]), col=adjustcolor(col.female, alpha.f=0.5))
polygon(density(p.m4b.F[[1]][,2]), col=adjustcolor(col.male, alpha.f=0.5))
polygon(density(p.m4b.F[[1]][,3]), col=adjustcolor(col.both, alpha.f=0.5))
legend("topright", fill=c(adjustcolor(col.female, alpha.f=0.5), adjustcolor(col.male, alpha.f=0.5), adjustcolor(col.both, alpha.f=0.5)), border="black", legend=c("Females only", "Males only", "Both sexes"), bty="n", cex=1.5)

# h) philo = M
dens(p.m1[[1]][,1], xlab="Predicted probability", ylab="Density", main="h) Philopatry = Males", col="white", ylim=c(0,3), xlim=c(0,1), cex.main=1.5, cex.axis=1.2, cex.lab=1.2)
polygon(density(p.m4b.M[[1]][,1]), col=adjustcolor(col.female, alpha.f=0.5))
polygon(density(p.m4b.M[[1]][,2]), col=adjustcolor(col.male, alpha.f=0.5))
polygon(density(p.m4b.M[[1]][,3]), col=adjustcolor(col.both, alpha.f=0.5))
legend("topright", fill=c(adjustcolor(col.female, alpha.f=0.5), adjustcolor(col.male, alpha.f=0.5), adjustcolor(col.both, alpha.f=0.5)), border="black", legend=c("Females only", "Males only", "Both sexes"), bty="n", cex=1.5)

# i) philo = B
dens(p.m1[[1]][,1], xlab="Predicted probability", ylab="Density", main="i) Philopatry = Both", col="white", ylim=c(0,3), xlim=c(0,1), cex.main=1.5, cex.axis=1.2, cex.lab=1.2)
polygon(density(p.m4b.B[[1]][,1]), col=adjustcolor(col.female, alpha.f=0.5))
polygon(density(p.m4b.B[[1]][,2]), col=adjustcolor(col.male, alpha.f=0.5))
polygon(density(p.m4b.B[[1]][,3]), col=adjustcolor(col.both, alpha.f=0.5))
legend("topright", fill=c(adjustcolor(col.female, alpha.f=0.5), adjustcolor(col.male, alpha.f=0.5), adjustcolor(col.both, alpha.f=0.5)), border="black", legend=c("Females only", "Males only", "Both sexes"), bty="n", cex=1.5)
dev.off()

```